SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-11 docs/questioning.tex
added the last paragraph of the intro

  By comparing the existing defenses and identifying their common
  characteristics, we help: a) researchers and practitioners to choose
  or modify a mechanism according to their needs, and b) designers of
  new approaches in developing more efficient mechanisms.
% dimitro@dimitro: change the above accordingly.

@@

Such attacks include Cross-Site Scripting ({\sc xss})
attacks~\cite{SG07}, {\sc sql} injection attacks~\cite{RL12b},
Cross-Site Request Forgery ({\sc csrf}) attacks~\cite{LZRL09}, and
others. Attacks like these have been topping the vulnerability lists
of numerous bulletin providers like the Open Web Application Security
Project\footnote{\url{https://www.owasp.org/index.php/Category:OWASP_Top_Ten_Project}}
({\sc owasp}) and {\sc
  mitre}\footnote{\url{http://cwe.mitre.org/top25/}} for several
years. Consider the case of {\sc owasp}'s Top Ten project whose main
goal is to raise awareness about web application security by
identifying some of the most critical risks facing organizations. The
Top Ten project is popular, referenced by numerous researchers. In its
three consecutive Top Ten lists (2007, 2010, 2013), different
source code-driven injection attacks dominate the top five
positions. Malicious users find new ways~\cite{HNSHS12,DKH14}
to bypass defense mechanisms
by using a variety of techniques despite the numerous countermeasures
that are being introduced. Note that the number of systems developed
to counter {\sc sql} injection attacks until 2006 was more than
twenty~\cite{HVO06}. Since then the number has doubled. Researchers
have also indicated that the number of such attacks is steadily
increasing in recent years~\cite{SSL12}.

@@

The rest of the paper is organized as follows. {\sc tba}.

@@

\section{Conclusions}

\begin{itemize}
\item Cite~\cite{DKH14}.
\item We believe that our research may facilitate researchers
or practitioners who would like to use one of the
aforementioned mechanisms and researchers who would like
to build new ones. Especially in the second case,
researchers can utilize our exploitation model as a
starting point to develop their approach.
\item We believe that forming a
standard way to test such mechanisms in terms
of accuracy and computational performance
would be one of the reasons of adopting them.
\end{itemize}

>>>>

  By comparing the existing defenses and identifying their common
  characteristics, we help: a) researchers and practitioners to choose
  or modify a mechanism according to their needs, and b) designers of
  new approaches in developing more efficient mechanisms.

@@

Such attacks include Cross-Site Scripting ({\sc xss})
attacks~\cite{SG07}, {\sc sql} injection attacks~\cite{RL12b},
Cross-Site Request Forgery ({\sc csrf}) attacks~\cite{LZRL09}, and
others. Attacks like these have been topping the vulnerability lists
of numerous bulletin providers like the Open Web Application Security
Project\footnote{\url{https://www.owasp.org/index.php/Category:OWASP_Top_Ten_Project}}
({\sc owasp}) and {\sc
  mitre}\footnote{\url{http://cwe.mitre.org/top25/}} for several
years. Consider the case of {\sc owasp}'s Top Ten project whose main
goal is to raise awareness about web application security by
identifying some of the most critical risks facing organizations. The
Top Ten project is popular, referenced by numerous researchers. In its
three consecutive Top Ten lists (2007, 2010, 2013), different
source code-driven injection attacks dominate the top five
positions. Malicious users find new ways to bypass defense mechanisms
by using a variety of techniques despite the numerous countermeasures
that are being introduced. Note that the number of systems developed
to counter {\sc sql} injection attacks until 2006 was more than
twenty~\cite{HVO06}. Since then the number has doubled. Researchers
have also indicated that the number of such attacks is steadily
increasing in recent years~\cite{SSL12}.

@@

The rest of the paper is organized as follows.
Section~\ref{sec:attacks} provides the exploitation model
of application attacks based on source code injection.
Section~\ref{sec:dimensions} introduces the dimensions
on which we base the analysis of the various defenses.
Our categorization and analysis is presented in
Section~\ref{sec:defs} and a discussion is provided in
Section~\ref{sec:discussion}. Finally,
Section~\ref{sec:lessons-learned} highlights
some lessons learned from our observations
and Section~\ref{sec:conclusion} concludes the paper.

@@

\section{Conclusions}
\label{sec:conclusion}

\begin{itemize}
\item Cite~\cite{HNSHS12,DKH14}.
\item We believe that our research may facilitate researchers
or practitioners who would like to use one of the
aforementioned mechanisms and researchers who would like
to build new ones. Especially in the second case,
researchers can utilize our exploitation model as a
starting point to develop their approach.
\item We believe that forming a
standard way to test such mechanisms in terms
of accuracy and computational performance
would be one of the reasons of adopting them.
\end{itemize}
